Measurement of nuclear excitation functions for proton induced reactions (E\texorpdfstring{$_{\text{p}}$\,=\,}{Ep = 40--90}40--90 MeV) on natural Nb

### 2018-04-05 nb_px_paper/nb_px_paper.tex
Broke Nb(p,x) paper into container w/ separate body text, appendices, and abstract, to be included in dissertation.  Still compiles into equivalent final PDF.

\usepackage{xfrac}
\usepackage{lmodern}
\usepackage[hidelinks]{hyperref}
% \usepackage{cool}
% \usepackage{cancel}
\usepackage{microtype}
\usepackage{listings}
\usepackage{mcode}
\usepackage [autostyle, english = american]{csquotes}
% \usepackage{longtable}
\usepackage{subcaption}
\usepackage{booktabs,siunitx}
\usepackage{gensymb}
\usepackage[normalem]{ulem}

@@

\usepackage{lineno}

@@

@@

\newcommand{\subfigimg}[4][,]{%
  \setbox1=\hbox{\includegraphics[#1]{#3}}% Store image in box
  \leavevmode\rlap{\usebox1}% Print image
  \rlap{\hspace*{#4pt}\raisebox{\dimexpr\ht1-2\baselineskip}{#2}}% Print label
  \phantom{\usebox1}% Insert appropriate spcing
}
% \subfigimg[scale=0.59]{a)}{./figures/after_minimization_plot_alt.pdf}{80pt}

@@

@@

% Intermediate-energy proton beams are used to produce a wide range of radionuclides for use in medical treatments and research.  
% However, reaction modeling in this energy range remains largely untested, and there is a paucity of monitor reactions in this energy range needed to establish beam characteristics  for quantitative cross section measurements.  
% To address this need, a
A stack  of thin Nb 
% , Cu, and Al monitor 
foils was irradiated with the 100 MeV proton beam at  Los Alamos National Laboratory's Isotope Production Facility,  to investigate the \ce{^{93}Nb}(p,4n)\ce{^{90}Mo} nuclear reaction as a  monitor for intermediate energy proton experiments and to benchmark state-of-the-art reaction model codes.
% A stacked target of natural Nb, Cu, and Al thin foils were irradiated by 100 MeV protons at the Los Alamos National Laboratory's Isotope Production Facility.
% The irradiation was motivated by interest in the characterization of the \ce{^{93}Nb}(p,4n)\ce{^{90}Mo} reaction as a new monitor reaction standard for intermediate-energy protons.
A set of 38 measured  cross sections for  \ce{^{nat}Nb}(p,x) and  \ce{^{nat}Cu}(p,x) reactions between 40--90 MeV, as well as 5 independent measurements of isomer branching ratios, are reported. 
% The measurements are 
These are useful in medical and basic science radionuclide productions at intermediate energies. 
% Cross sections were measured using the well-characterized 
The
% \ce{^{nat}Al}(p,x)\ce{^{22}Na}, \ce{^{nat}Al}(p,x)\ce{^{24}Na}, 
\ce{^{nat}Cu}(p,x)\ce{^{56}Co}, \ce{^{nat}Cu}(p,x)\ce{^{62}Zn}, and \ce{^{nat}Cu}(p,x)\ce{^{65}Zn}  reactions were used to
determine proton fluence, and all activities were quantified using HPGe spectrometry.
Variance minimization techniques were employed to reduce systematic uncertainties in proton energy and fluence, improving the reliability of these measurements. 
The measured cross sections are shown to be in excellent agreement with  literature values, and have been measured with improved precision compared with previous measurements.
This work also reports the first measurement of the  \ce{^{nat}Nb}(p,x)\ce{^{82m}Rb} reaction, and of the independent cross sections for    
% \ce{^{nat}Cu}(p,x)\ce{^{52\text{m}}Mn}, 
\ce{^{nat}Cu}(p,x)\ce{^{52\text{g}}Mn} and \ce{^{nat}Nb}(p,x)\ce{^{85\text{g}}Y} in the 40--90 MeV region.
% \textred{
% Due to \ce{^{nat}Si}(p,x)\ce{^{22,24}Na} contamination  by  activation of the silicone adhesive used for sealing foil packets, the \ce{^{nat}Al}(p,x)\ce{^{22}Na} and \ce{^{nat}Al}(p,x)\ce{^{24}Na}  monitor reactions  were excluded, in the interest of surety, from proton fluence determination.
% }
% \textred{
% To avoid inadvertently reporting enhanced proton fluence due to
The effects of  \ce{^{nat}Si}(p,x)\ce{^{22,24}Na} contamination, arising from  silicone adhesive in the Kapton tape used to encapsulate the aluminum monitor foils, is also discussed as a cautionary note to future stacked-target cross section measurements.
% strongly discouraged.
% }
% Comparisons against the 
\emph{A priori} predictions of the reaction modeling codes  CoH, EMPIRE, and TALYS are compared with experimentally measured values and used to explore the differences between codes for the
% impact of pre-equilibrium particle emission  for the 
% 40--90 MeV 
\ce{^{nat}Nb}(p,x) and  \ce{^{nat}Cu}(p,x) reactions.

% \begin{description}
% \item[Usage]
% Secondary publications and information retrieval purposes.
% \item[PACS numbers]
% May be entered using the \verb+\pacs{#1}+ command.
% \item[Structure]
% You may use the \texttt{description} environment to structure your abstract;
% use the optional argument of the \verb+\item+ command to give the category of each item. 
% \end{description}
\end{abstract}

@@

%%
%% Start line numbering here if you want
%%
\linenumbers

%% main text 
\section{Introduction} \label{sec:intro}

% Referring to abstract:
% % \comment{Stephen:  Not strictly true if you've omitted Na22 and Co56 from your fluence determination.  Update monitors here following discussion.}
% 
% 
% \comment{Comment on the Si production here?  (see red text)}
% 
% \comment{Add extra physics language with Lee.}

% \comment{cite theranostic papers, etc}

Every year, approximately 17 million nuclear medicine procedures (both diagnostic and therapeutic) are performed in the U.S. alone 
% ,  which has made incredible strides in improving our ability to detect and treat a variety of life-threatening diseases 
\cite{Delbeke2011,NSACIsotopesSubcommittee2015}.
% The vast majority
Most of the radionuclides currently used for these procedures are produced 
% in the field's array of
by low- (E \textless\ 30 MeV / A) and intermediate-energy (30 \textless\ E \textless\ 200 MeV / A) accelerators, 
% capabilities, which routinely produce many of the staple medical radionuclides, such as 
e.g., \ce{^{11}C}, \ce{^{18}F}, \ce{^{68}Ga}, \ce{^{82}Rb}, and \ce{^{123}I}. 
These accelerators also produce 
% , as well as many  
% of the 
non-medical radionuclides with commercial value, such as  \ce{^{32}Si}, \ce{^{73}As}, \ce{^{95m}Tc}, and  \ce{^{109}Cd} \cite{international2009iaea,schlyer2008cyclotron}. 
% \comment{Should \enquote{intermediate-energy} be less than 200 MeV, or 100 MeV?  I find conflicting descriptions in the literature.\\Lee:  I believe that 60 MeV is considered as the transition point\\ Stephen: In this context, I would make this definition based on what machines in the US are routinely used for medical isotope production - based on this, I agree with 200 MeV. }
% The future of nuclear medicine would appear to be the paradigm of personalized medicine --- targeted radionuclide therapy to spare healthy tissue \cite{Mulford2005,Qaim201731}, and theranostic medicine, which pairs an imaging isotope with a therapeutic isotope (frequently, of the same element), to provide simultaneous, real-time dose delivery and verification, leading to drastic reductions in prescribed patient dose \cite{Muller2014,Bentzen2005,Srivastava2012}. 
% Other variants of theranostic medicine exist, including pre-imaging for treatment planning, or delivery of a single compound with different radioelements for imaging/therapy where the inter-element biodistribution has been validated.  
Novel applications are being explored for several radionuclides whose production methodologies are not established, but their production requires accurate, high-fidelity cross section data.
% \cite{Qaim201731}. 
% Move next sentence to Fe paper
% Many of these applications focus on theranostics, the use of chemically identical (or similar) imaging and therapeutic radiopharmaceuticals for treatment of disease. 
Candidate isotopes to meet these needs 
% of personalized medicine 
have been identified based on their chemical and radioactive decay properties \cite{NSACIsotopesSubcommittee2015,Qaim201731,bernstein2015nuclear}, and a series of campaigns are underway to perform targeted, high-priority measurements of thin-target cross sections and thick-target integral yields.
These studies will serve to facilitate the production of clinically relevant quantities of radioactivity.

Accurate cross section measurements using  activation methods benefit from well-characterized monitor reactions.  
Currently there is 
% , which  currently
a paucity of such data at intermediate energies, and much of what exists have  high uncertainties (\textgreater15\%).
% One significant obstacle to both high-fidelity measurements of production cross sections for emerging medical radionuclides, as well as conventional isotope production, is a lack of well-characterized  monitor reaction standards.  
% This is particularly true for higher-energy charged particle beams, where there is currently a paucity of such data. 
% Lee - cut?
Indeed, the development of new monitor reaction standards and the improved evaluation of existing standards is one of the areas of greatest cross-cutting need for nuclear data \cite{bernstein2015nuclear}. 
% Charged particle monitor reaction data currently exists for several low-to-intermediate energy charged particle beams (E \textless\ 50 MeV / A), but even the experimental data used for this evaluation are  sparse above approximately 30 MeV / A and  uncertainties in experimental cross sections are large (6--15\%) \cite{gul2001charged}. 
% While work is needed to improve upon existing monitor reaction data, the development of n
% Lee - cut?
New reactions can expand the available range of options for the monitoring of charged particle beams.
This work 
% in particular seeks to improve this range of options by 
is an attempt to characterize a new monitor reaction for  proton beams in excess of 40 MeV, for possible use at isotope production facilities such as the  Brookhaven Linac Isotope Producer (BLIP) at Brookhaven National Laboratory, 
% IPF
the Isotope Production Facility (IPF) at  Los Alamos National Laboratory, or the Separated Sector Cyclotron at the 
% iThemba LABS
iThemba Laboratory for Accelerator Based Sciences.
% \comment{Stephen: I'm having a hard time following this paragraph. Some of your syntax overlaps significantly with nuclear medicine \& medical physics terminology with different intended meanings. For example 'dosimetry' is typically taken to mean the measurement of absorbed energy per unit mass (J/kg) and associated measurements/specifications. Another example, 'dosimetry standard' is used quite often when referring to NIST air kerma reference standards which are the bedrock of Accredited Dosimetry Calibration Lab (ADCL) measurements. As you are more familiar with classic Nuclear Physics writing, perhaps you better know how this language will be interpreted. }

% % 
% 
% Most of this should be more appropriate for the PhD thesis?
% 
% % 
% Activation analysis is one of the most fundamental measurement techniques in experimental nuclear physics, as it is a simple and straightforward method to probe the structure and behavior of nuclear matter,  dating back to the infancy of the field \cite{ehmann1993radiochemistry,krüger1971principles}. 
% % All activation measurements involve the analysis and quantification of decaying radioactive nuclei created through irradiation via ionizing radiation \cite{ehmann1993radiochemistry,krüger1971principles}.
% % \comment{Lee:  I think that you might want to mention a connection to BLIP, IPF, iThemba etc. here, and make it clear that you're dealing with protons only, not neutrons.  }
% Monitor reactions have  historically been part of such activation experiments, and serve two valuable purposes for charged particle-induced reactions, depending upon the energy regime.  
% % \comment{Stephen:  Move much of the remaining intro section into the Discussion, for brevity?}
% Between the reaction's energetic threshold  and the end of its compound peak, the magnitude and shape of the excitation function changes rapidly with increasing energy, making it useful for determining the energy distribution of particles which have traversed a thin irradiated target.
% This is particularly the case when comparing  monitor reactions leading to two distinct residual nuclei from the same target, such as the $^\text{nat}$Cu(p,x)\ce{^{62}Zn} and $^\text{nat}$Cu(p,x)\ce{^{63}Zn} reactions \cite{gul2001charged}.
% This is extremely valuable, as it allows the screening and minimization of systematic errors based on energy determination, though this energy sensitivity  precludes their reliability as a beam current monitor.  
% In the higher energy  of the reaction's pre-equilibrium tail, the excitation function becomes  smooth and generally flat as a function of energy.
% This  offers little-to-no energy sensitivity, but  is extremely useful for determining the integral beam current. 
% While cross section measurements often use external beam current monitors (such as an inductive pickup upstream of a target, or an electrically-isolated target in a Faraday cup), these measure the integrated current incident upon the \enquote{front} (upstream) of the target assembly.
% % For the case of stacked-target activation experiments, commonly employed to measure cross sections at multiple energies  in a single activation, external beam current monitors can only measure the integral current incident upon the \enquote{front} (upstream) of the target stack.
% % In these experiments, a
% A series of monitor foils at each energy position allows one to indirectly measure the integral current at each position within the stack, reducing systematic errors in observed cross section magnitude, but with reduced precision compared to direct measurement using a well-characterized suppressed Faraday cup.
% % \comment{Stephen:  ``and precision, unfortunately ''.  Update post-discussion.}
% Both of these purposes make well-characterized monitor reactions an invaluable asset to any activation experiment.

% In theory, nearly any radioisotope can serve as a reaction monitor, but 
% those desired to be classified as a 
Desirable monitor reactions 
% standard 
possess several hallmark characteristics,  
% The primary factor involved in selecting a new monitor is ensuring that the desired radionuclide emit  at least one (preferably multiple, to ensure accurate radionuclide identification) distinct decay gamma-rays which can be used to uniquely identify it during post-activation assay.  
% Primarily, this means selecting a radionuclide product with 
% a number of 
including intense and distinct gamma-rays, 
% with high intensities,  
which can be used to uniquely identify it during post-activation assay, and lifetimes long enough to enable removal after a reasonable length irradiation.    
% The decay radiation should preferably have high intensities, so that they show up as strong peaks, and minimize the amount of time needed to count the activated target in order to achieve acceptable counting statistics. 
% \comment{Stephen:  These next 2 paragraphs are better suited for the discussion, specifically addressing how this problem affects your particular experiment. }
Care should also be taken to avoid cases where two radionuclides which are produced by two different reactions on the same monitor foil lead to states in the same daughter nuclide.  
For example, \ce{^{48}V}  ($t_{1/2}$ = 15.97 d, $\epsilon=100\%$ to \ce{^{48}Ti}) and \ce{^{48}Sc}  ($t_{1/2}$ = 43.67 h, $\beta^-=100\%$ to \ce{^{48}Ti}) can both be formed via $^\text{nat}$Ti(p,x) reactions, yielding the same 983.52 keV transition in \ce{^{48}Ti} \cite{Burrows2006}.
% Fortunately, these cases can occasionally be mitigated by either using a difference in half-life between the two feeding pathways to allow one to decay out, or by using a distinct gamma-ray from one of the two isobar nuclei to subtract out the activity associated with it (such as the $E_\gamma=1037.522$ keV, $I_\gamma=97.6\%$ line in the decay of \ce{^{48}Ti}) \cite{Burrows2006}.
% However, this approach propagates larger uncertainties into the final activity of the desired monitor nucleus, so in principle it is far preferred to choose a monitor reaction which does not have overlapping gamma-rays from another isobar nucleus.
% Another important decay factor to consider is that of the half-life of the desired monitor nucleus.
% Ideally, the nucleus has a lifetime which is comparable to that of the reaction products being studied, and sufficiently long-lived to ensure that it may be quantified  conveniently 
% and leisurely 
% following end-of-bombardment.
% without the majority if it decaying away.
% In addition, it is preferred that the lifetime be comparable to that of the reaction products being studied. 
% For proper quantification, i
It is also of vital importance that the proposed monitor nucleus have well-characterized decay data.
This includes a precise and well-established half-life,  
% needed to  correct for decay losses, 
as well as well-characterized decay gamma-ray intensities.
% In practice, the weakest components of decay data are often the gamma-ray intensities, which can routinely have uncertainties of 5\% or more.
% Since this uncertainty is propagated in quadrature from the activity of both the monitor reaction and the reaction product being studied, choosing a monitor with a well-established gamma-ray intensity can make a significant reduction in measured cross section uncertainties.
From a targetry  perspective, it is preferable to use a naturally mono-isotopic target that is readily available
% readily commercially available at an affordable price and is 
and  chemically inert.
% --- any significant chemical changes during target preparation (significant oxidation, etc.) will affect the target's areal density, systematically changing the measured integral current. 
% Structurally, the target material should be malleable and supportive to be able to be formed into a thin target.
% For charged particle reactions,  energy degradation scales with target areal density,  broadening the energy spectrum downstream of the target.
% However, since the monitor reaction yield also scales with target areal density, the use of a target which is too thin may provide insufficient counting statistics during decay spectrometry.
% For reference, a monitor foil of approximately 25 mg/cm$^2$ provides a good compromise, with less than 100 keV degradation for a proton energy of 100 MeV, and less than 200 keV at 40 MeV.
Targets which can be formed into a wide thickness range are convenient, as selection is subject to the context of an experiment, seeking to maximize thickness without overly perturbing the energy uncertainty of  measurements.
% These are the primary characteristics involved in choosing an appropriate target for a monitor reaction
% \comment{Stephen:  This is also a discussion point. If you're trying to introduce the purpose of this paper, i.e. the establishment of a new monitor reaction, I would try to condense paragraphs 3--9 into two paragraphs: one paragraph explaining what a monitor reaction is used for, and the other describing considerations relevant to the use of a monitor reaction. The rest of this content can be included in the discussion if you feel it is necessary.}
Lastly, and perhaps most importantly for high-energy monitor reaction applications, it is  of utmost importance to choose a reaction channel which cannot be populated via secondary particles incident upon the monitor target.
Typically, this is  mostly a concern for secondary neutrons produced through (z,xn) reactions, 
% on upstream targets, degraders, and stack materials, to avoid monitor reactions which can be populated through (n,x) reactions on the target.
% Any
but any monitor reaction channel which can be populated by anything other than the primary beam should be avoided, as it is often 
% a laborious task 
difficult to accurately and unambiguously separate out the fraction of secondary particles contributing to the total activation.

One  reaction which satisfies these requirements is that of a new, intermediate-energy proton monitor reaction standard based on \ce{^{93}Nb}(p,4n)\ce{^{90}Mo}. 
Niobium is naturally mono-isotopic, readily  available commercially in high purity, is fairly chemically inert, and can easily be rolled down to foils as thin as 1 $\micro$m.  
\ce{^{90}Mo} also has 
% excellent decay properties ---
a sufficiently long lifetime ($\epsilon=100\%, t_{1/2}=5.56 \pm 0.09$ h \cite{Browne1997})  
% allows it to be counted at leisure without fear of the product \ce{^{90}Mo} decaying away excessively between end-of-bombardment and the start of counting, and it possesses
and seven strong, distinct gamma lines (notably its 122.370 keV [$I_\gamma = 64 \pm 3\%$] and 257.34 keV [$I_\gamma = 78 \pm 4\%$] lines) which can be used to uniquely and easily   quantify \ce{^{90}Mo} production. 
In addition,  \ce{^{90}Mo} is completely immune from (n,x) production on  \ce{^{93}Nb}, being produced only via the primary proton beam, and the \ce{^{90}Mo} decay lines can only be observed in its decay, as its daughter, \ce{^{90}Nb}, is also unstable and decays via $\epsilon$ to stable \ce{^{90}Zr}.

The purpose of the present work is to  measure the production of the long-lived radionuclide \ce{^{90}Mo}  
% ($t_{1/2}=5.56 \pm 0.09$ h \cite{Browne1997}) 
via the $^\text{nat}$Nb(p,x) reaction. 
In addition to the $^\text{nat}$Nb(p,x)\ce{^{90}Mo} measurement, this experiment has also yielded measurements of 37 other (p,x) production cross sections between 40--90 MeV  for a number of additional reaction products, including several emerging radionuclides with medical applications.
% These include the non-standard positron emission tomography (PET) agents \ce{^{57}Ni}  ($t_{1/2}=35.60\pm0.06$ h \cite{Bhat1998}), \ce{^{64}Cu} ($t_{1/2}=12.701 \pm 0.002$ h \cite{Singh2007}), \ce{^{86}Y}  ($t_{1/2}=14.74\pm0.02$ h \cite{NEGRET20151}), \ce{^{89}Zr} ($t_{1/2}=78.41\pm0.12$ h \cite{Singh2013}),  \ce{^{90}Nb} ($t_{1/2}=14.60 \pm 0.05$ h \cite{Browne1997}),  and the diagnostic agent \ce{^{82\text{m}}Rb} ($t_{1/2}=6.472\pm0.006$ h \cite{Tuli2003}). 
These include the non-standard positron emitters \ce{^{57}Ni}, \ce{^{64}Cu},  \ce{^{86}Y}, \ce{^{89}Zr},  \ce{^{90}Nb}, 
% the $\beta^-$-therapy agent  \ce{^{64}Cu},  
and the diagnostic agent \ce{^{82\text{m}}Rb}.

%   \comment{The following paragraph should only be included if we decide to touch on spin physics in this manuscript, or split it into a follow-on PhysRev C, etc.}
%   
%   \comment{Stephen:  If included in this paper, I would move to the discussion. It's not clear yet in the paper that you have the data required to make these determinations.}

In addition to providing a potentially highly-valuable beam monitor, the Nb(p,x) reactions offer an opportunity to study the angular momentum deposition via pre-equilibrium reactions and the spin distribution in g$_{9/2}$ subshell nuclei via the observation of isomer-to-ground state ratios.  
Measurements of isomer-to-ground state ratios have been used for over 20 years to probe the spin distribution of excited nuclear states in the A\,$\approx$\,190 region \cite{PhysRevC.73.034613,PhysRevC.45.1171}.
These include the \ce{^{52\text{m}}Mn} ($t_{1/2}=21.1\pm0.2$\,m; J$^\pi=2^+$) to \ce{^{52\text{g}}Mn}  ($t_{1/2}=5.591\pm0.003$\,d; J$^\pi=6^+$), \ce{^{58\text{m}}Co} ($t_{1/2}=9.10\pm0.09$\,h; J$^\pi=5^+$) to \ce{^{58\text{g}}Co}  ($t_{1/2}=70.86\pm0.06$\,d; J$^\pi=2^+$),  \ce{^{85\text{m}}Y} ($t_{1/2}=4.86\pm0.13$\,h; J$^\pi=\sfrac{9}{2}^+$) to \ce{^{85\text{g}}Y}  ($t_{1/2}=2.68\pm0.05$\,h; J$^\pi=\sfrac{1}{2}^-$),  \ce{^{87\text{m}}Y} ($t_{1/2}=13.37\pm0.03$\,h; J$^\pi=\sfrac{9}{2}^+$) to \ce{^{87\text{g}}Y}  ($t_{1/2}=79.8\pm0.3$\,h; J$^\pi=\sfrac{1}{2}^-$),  and \ce{^{89\text{m}}Nb} ($t_{1/2}=66\pm2$\,m; J$^\pi=\sfrac{1}{2}^-$) to \ce{^{89\text{g}}Nb}  ($t_{1/2}=2.03\pm0.07$\,h; J$^\pi=\sfrac{9}{2}^+$)  ratios \cite{Dong2015,Nesaraja2010,Singh2014,Johnson2015,Singh2013}.

The measurements described in this paper involve the use of multiple monitor reactions in conjunction with statistical calculations and proton transport simulations to reduce systematic uncertainties in beam energy assignments, leading to some of the first and most precise measurements  for many of the excitation functions reported here. 
By expanding the available set of monitor reaction standards and well-characterized isotope production excitation functions, this work should help optimize medical isotope production modalities, making more options   available for modern medical imaging and cancer therapy.

\section{Experimental methods and materials}\label{sec:experiment}

% While the reactions and mass region being explored in this work differ from the recent work of Graves \etal, much of the analysis described in the present work 
The work described herein follows the  methods established by Graves \etal\ for the measurement of cross sections in stacked target irradiations   \cite{Graves2016}.

\subsection{Stacked-target design }\label{sec:target_design}

% \comment{Regex to replace all hard figure references with LaTeX cross-references  [F,f]igure[^s*}]     }

A stacked-target design was utilized for this work in order that the (p,x) cross sections for each reaction channel could be measured at multiple energy positions in a single irradiation \cite{Cumming1963}. 
% For targets, a
A series of nominal 25 \micro m \ce{^{nat}Nb} foils (99.8\%, lot \#T23A035), 25 \micro m \ce{^{nat}Al} foils (99.999\%, lot \#M06C032), and 50 \micro m \ce{^{nat}Cu} foils (99.9999\%, lot \#N26B062) were used (all from Alfa Aesar, Ward Hill, MA, 01835, USA) targets were used.
Six foils of each metal were cut down to 2.5 x 2.5 cm squares and characterized --- for each foil, length and width measurements were taken at four different locations using a digital caliper (Mitutoyo America Corp.), thickness measurements were taken at four different locations using a digital micrometer (Mitutoyo America Corp.), and four mass measurements were taken using an analytical balance after cleaning the foils with isopropyl alcohol.
Using these length, width, and mass readings, the areal density and its uncertainty (in mg/cm$^2$) for each foil was calculated.
% , along with the propagated uncertainty in areal density.
The foils were tightly sealed into \enquote{packets} using two pieces of  3M 5413-Series Kapton polyimide film tape --- each piece of tape consists of 43.2 \micro m of a silicone adhesive (nominal 4.79 mg/cm$^2$) on 25.4 \micro m of a polyimide backing (nominal 3.61 mg/cm$^2$).
The sealed foils were mounted over the hollow center of a 1.575 mm-thick plastic frame.
One \ce{^{nat}Al}, one \ce{^{nat}Cu}, and one \ce{^{nat}Nb} mounted foil were bundled together using baling wire for each energy position.
These foil packet bundles were lowered into the beamline by inserting them into a  water-cooled production target box.
% These six foil packet bundles were inserted into one of six  
The box, seen in \autoref{fig:target_stack}, is machined from 6061 aluminum alloy, has a thin (0.64 mm) Inconel beam entrance window, and  contains 6 \enquote{energy positions} for targets, formed by  5 slabs of 6061 aluminum alloy (previously characterized) which serve as proton energy degraders  between energy positions.
% At both the front and rear of the target stack's foils, a 316 stainless steel foil is inserted to serve as a beam profile monitor --- after end-of-bombardment (EoB), decay radiation emitted from these activated stainless steel foils were used to develop radiochromic film (Gafchromic EBT3), revealing the spatial profile of the beam entering and exiting the stack.
After loading all targets in the stack, the lid of the target box is sealed in place, using an inset o-ring to create a water-tight seal, and the box is lowered through a hot cell into the beamline, where it sits electrically isolated.
The specifications of the target stack design for this work is presented in \autoref{tab:stack_table}.

This target stack was assembled and irradiated at the Isotope Production Facility (IPF) at the Los Alamos National Laboratory (LANL), using the LANSCE linear accelerator. 
The stack was irradiated for approximately 2 hours with a nominal current of 1 mA, using a 50 \micro s pulse at a frequency of 2 Hz, for an anticipated integral current of 205.9 nAh.
The beam current, measured using an inductive pickup, remained stable under these conditions for the duration of the irradiation, with the exception of approximately 70\,s of downtime, which occurred approximately 3 minutes into irradiation.
The proton beam incident upon the stack's Inconel beam entrance window had an average energy of 100 MeV determined via time-of-flight, with an approximately Gaussian energy distribution width of 0.1 MeV --- this energy profile was used for all later analysis.
At the end of the irradiation, the target stack was withdrawn from the beamline into the IPF hot cell, where it was disassembled and the activated foils removed using robotic manipulators.
The activated foils were cleaned of all surface contamination, and transported to a counting lab for gamma spectrometry, which started approximately 6 hours following end-of-bombardment.

\begin{figure}
 \centering
 \includegraphics[width=0.5\linewidth,clip=true,trim=13cm 0cm 3cm 6cm]{./figures/IMG_1975.JPG}
 % IMG_1975.JPG: 3264x2448 pixel, 72dpi, 115.15x86.36 cm, bb=0 0 3264 2448
 \caption{\label{fig:target_stack}Photograph of the assembled IPF target stack, before the stack's o-ring lid was sealed in place. The baling wire handles affixed to each bunch of Al+Cu+Nb foils are visible in each energy position, to facilitate removal of activated foils via robotic manipulators in the IPF hot cell. The circular Inconel beam entrance aperture is visible in the bottom center of the photograph.  }
\end{figure}

% Please add the following required packages to your document preamble:
% \usepackage{booktabs}
\begin{table}
\centering
\caption{Specifications of the  target stack design in the present work. The proton beam enters the stack upstream of the 249.8 \micro m SS profile monitor, and is transported through the stack in the order presented here. The 6061 aluminum degraders have a measured density of approximately 2.80 g/cm$^3$. Their areal densities were determined using the variance minimization techniques described  in this work  and the earlier paper by Graves \etal\ \cite{Graves2016}. At both the front and rear of the target stack's foils, a 316 stainless steel foil is inserted to serve as a beam profile monitor --- after end-of-bombardment (EoB), decay radiation emitted from these activated stainless steel foils were used to develop radiochromic film (Gafchromic EBT3), revealing the spatial profile of the beam entering and exiting the stack.}
\label{tab:stack_table}
\small
\begin{tabular}{@{}llll@{}}
\toprule
% Target Layer       & Nominal Thickness & Measured thickness (mg/cm\textasciicircum 2) & Thickness Uncertainty (\%) \\ \midrule
Target layer       & \begin{tabular}[c]{@{}l@{}}Measured \\ thickness\end{tabular} & \begin{tabular}[c]{@{}l@{}}Measured areal\\density (mg/cm$^2$)\end{tabular} & \begin{tabular}[c]{@{}l@{}}Areal density \\ uncertainty (\%)\end{tabular} \\ \midrule
SS profile monitor & 249.8 \micro m         & 194.56                                      & 0.29                      \\
Al-1               & 25.0 \micro m          & 6.52                                        & 0.72                      \\
Cu-1               & 61.3 \micro m          & 53.74                                       & 0.15                      \\
Nb-1               & 30.0 \micro m          & 23.21                                       & 0.17                      \\
Al Degrader 01     & 4.96 mm           & -                                            & -                          \\
Al-2               & 25.5 \micro m          & 6.48                                        & 0.36                      \\
Cu-2               & 61.8 \micro m          & 53.85                                       & 0.17                      \\
Nb-2               & 30.8 \micro m          & 22.91                                       & 0.17                      \\
Al Degrader 02     & 4.55 mm           & -                                            & -                          \\
Al-3               & 25.8 \micro m          & 6.47                                        & 0.31                      \\
Cu-3               & 61.5 \micro m          & 53.98                                       & 0.11                      \\
Nb-3               & 31.0 \micro m          & 22.91                                       & 0.24                      \\
Al Degrader 03     & 3.52 mm           & -                                            & -                          \\
Al-4               & 26.3 \micro m          & 6.51                                        & 0.41                      \\
Cu-4               & 61.3 \micro m          & 53.46                                       & 0.22                      \\
Nb-4               & 30.8 \micro m          & 22.55                                       & 0.25                      \\
Al Degrader 04     & 3.47 mm           & -                                            & -                          \\
Al-5               & 26.5 \micro m          & 6.48                                        & 0.29                      \\
Cu-5               & 61.5 \micro m          & 53.57                                       & 0.11                      \\
Nb-5               & 30.8 \micro m          & 22.11                                       & 0.25                      \\
Al Degrader 05     & 3.46 mm           & -                                            & -                          \\
Al-6               & 26.3 \micro m          & 6.48                                        & 0.62                      \\
Cu-6               & 62.0 \micro m          & 53.84                                       & 0.32                      \\
Nb-6               & 31.3 \micro m          & 22.12                                       & 0.13                      \\
SS profile monitor & 124.4 \micro m         & 101.34                                      & 0.23                      \\ \bottomrule
\end{tabular}
\end{table}

\subsection{Measurement of induced activities}\label{sec:spectroscopy}

% For consistency, a
A single detector was used in this measurement, an ORTEC GEM Series (model \#GEM10P4-70)  High-Purity Germanium (HPGe) detector.
The detector is a mechanically-cooled coaxial p-type HPGe with a 1 mm aluminum window, and a 49.2 mm diameter, 27.9 mm long crystal.
Samples were counted at fixed positions ranging 4.5--83.5  cm (5\% maximum permissible dead-time) from the front face of the detector, with a series of standard calibration sources used to determine energy, efficiency, and pileup calibrations for each position.
The foils were counted  for a period of 2 weeks following end-of-bombardment (EoB), to accurately quantify all induced activities,  with dead time never exceeding 5\%.
An example of one of the gamma-ray spectra collected in such a fashion is shown in \autoref{fig:gspec}.
For all spectra collected, net peak areas were fitted using the gamma spectrometry analysis code UNISAMPO \cite{Aarnio2001}, which has been shown to perform best in comparisons with other common analysis codes \cite{Jackman2014}.
%, due to its peak fitting algorithms and incorporation  of calibrated detector-specific peak shapes and widths.

\begin{figure}
 \centering
 \includegraphics[width=6in]{./figures/sample_gspec.pdf}
 % sample_gspec.pdf: 489x257 pixel, 72dpi, 17.25x9.07 cm, bb=0 0 489 257
 \caption{A gamma spectrum, collected from an activated Nb foil at approximately 80 MeV. While the majority of observed reaction products are visible in this spectrum,  the \ce{^{90}Mo} decay lines, which form the basis of the \ce{^{93}Nb}(p,x)\ce{^{90}Mo} monitor reaction, are high in intensity and clearly isolated from surrounding peaks.}
 \label{fig:gspec}
\end{figure}

Following  acquisition, the decaying product nuclei corresponding to each observed peak in the collected spectra were identified.
The calibrated detector efficiencies, along with gamma-ray intensities for each transition and  corrections for gamma-ray attenuation within each foil packet, were used to convert the net  counts in each fitted gamma-ray photopeak into an activity for the decay of the activation products.  
% For reference, t
The nuclear decay data used in this work is tabulated in \autoref{tab:nudat_table_monitors} and \autoref{tab:nudat_table_nb} of \ref{data}.
Data for photon attenuation coefficients were taken from the XCOM photon cross sections database  \cite{berger2011xcom}.
% As nearly all of the product nuclei have multiple high-intensity gamma-rays, decay gamma-rays from the product nuclei were measured at multiple points in time (up to 2 weeks after EoB), as well as multiple independent activity measurements at each time point, based on each of its observed gamma-rays.
Decay gamma-rays from the product nuclei were measured at multiple points in time (up to 2 weeks after EoB), and as nearly all of the product nuclei have multiple high-intensity gamma-rays, this provided independent activity measurements at each time point.
% activity for each gamma-ray possesses a 
The total propagated uncertainty of the measured activity is the quadrature sum of the uncertainty in  fitted peak areas, uncertainty in detector efficiency calibration, and uncertainty in the gamma-ray branching ratio data.

>>>>

\usepackage{xfrac}
\usepackage{lmodern}
\usepackage[hidelinks]{hyperref}
% \usepackage{cool}
% \usepackage{cancel}
\usepackage{microtype}
\usepackage{listings}
\usepackage{mcode}
\usepackage [autostyle, english = american]{csquotes}
% \usepackage{longtable}
% \usepackage{subcaption}
\usepackage{booktabs,siunitx}
\usepackage{gensymb}
\usepackage[normalem]{ulem}

@@

% \usepackage{lineno}

@@

% Prevent ''overfull hbox'' warnings for < 5pt overflow 
% \hfuzz=10pt 
% \hfuzz\maxdimen

@@

\newcommand{\subfigimg}[4][,]{%
  \setbox1=\hbox{\noindent\includegraphics[#1]{#3}}% Store image in box
  \leavevmode\rlap{\usebox1}% Print image
  \rlap{\hspace*{#4pt}\raisebox{\dimexpr\ht1-2\baselineskip}{#2}}% Print label
  \phantom{\usebox1}% Insert appropriate spcing
}
% \subfigimg[scale=0.59]{a)}{./figures/after_minimization_plot_alt.pdf}{80pt}

\usepackage{subfig}
% Remove a), b), etc labels from subfigs
\captionsetup[subfigure]{labelformat=empty}

@@

\hyphenation{gamma-rays}

@@

\input{./nb_abstract_text}

\end{abstract}

@@

%%
%% Start line numbering here if you want
%%
% \linenumbers

\input{./nb_body_text}
